Deep Probabilistic Models for Camera Geo-Calibration

### 2018-09-02 chapters/introduction/introduction.tex
finish another run of editting

\subsection{Geo-Calibration for Feature Learning and Image
Understanding}
Full supervision algorithms are powerful tools to learn useful image
features. However, full supervision algorithms requires large number
of annotated data, which in many cases are either not available or
financially infeasible to obtain. On the other hand, images with free
annotations like time and locations are plentiful on the Internet.
To use these image resources for image feature learning, 
we explore two types of learning techniques that uses time and
locations as annotations: 1) {\em ground-to-aerial segmentation}, and 2)
{\em geo-temporal feature learning} with time/location tagged images.

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Segmentation:}
  Semantic segmentation plays an important role in image understanding.
  The training for semantic segmentation task requires a large number
  of annotated data.
  However, most large scale annotated datasets like ImageNet~\cite{ILSVRC15}
  and COCO~\cite{lin2014microsoft} are made of ground level images. By
  comparison, annotated datasets for aerial imagery are rare.
  %
  To deal with this problem, we proposed a
  DNN to learn to semantically segment aerial images with only
  ground-level annotations. Our method exploits the spatial
  correspondences between images in cross-view pairs. 
  In this work, we try to transfer the semantic knowledge from the
  ground domain to the aerial domain by identifying their latent
  geometric correspondences. Similar to {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective}
  which have been successfully applied in monocular depth estimation,
  our network learns the geometric projection from aerial to ground, and
  to semantically segment the aerial images jointly.
  We present the learning details in \chapref{crosstransf}
  \newline

  \item \textbf{Location and Time as Pretext Task:}
  Smart devices like cellphones and webcams becomes popular and most
  of them are equipped with clocks and GPS modules nowadays. Thanks to
  the development of social networks, researchers now can find
  a lot images online that are tagged with time and locations. In
  \chapref{whenwhere}, we propose an algorithm that treats the location and
  time as pretext task to learn useful image features.
  By learning to predict the geographic location and capture time of
  the query image, our network learns to extract geo-temporal features
  from the image.

>>>>

\subsection{Geo-Calibration for Feature Learning and Image
Understanding}
Full supervision algorithms are powerful tools to learn useful image
features. However, full supervision algorithms require large number
of annotated data, which takes a lot of human labors and is usually
unavailable.
On the other hand, images with annotations like tags and GPS locations
uploaded by individual users or captured automatically by smart
devices are plentiful on the Internet.
To use these image resources to understand the world,
we explore two approaches that use time and
locations as weak annotations: 1) {\em ground-to-aerial segmentation}, and 2)
{\em geo-temporal feature learning} with time/location tagged images.

\begin{itemize}[noitemsep]
  \item \textbf{Ground-to-Aerial Segmentation:}
  Semantic segmentation plays an important role in image understanding.
  The training for semantic segmentation task requires a large number
  of annotated data.
  However, most large scale annotated datasets like ImageNet~\cite{ILSVRC15}
  and COCO~\cite{lin2014microsoft} are mostly made of ground-level
  images. By comparison, annotated datasets for aerial imagery are rare.
  %
  To deal with this problem, we proposed a
  DNN to learn semantic segmentation for aerial images with only
  ground-level annotations. Our method exploits the spatial
  correspondences between images in the cross-view pair, where the
  aerial imagery and ground imagery are associated by location and
  geo-orientation.
  In this work, we transfer the semantic knowledge from the
  ground domain to the aerial domain by identifying their latent
  geometric correspondences. Similar to {\em
  Reprojection Losses}~\cite{garg2016unsupervised,
  godard2017unsupervised,zhou2017unsupervised, yan2016perspective},
  which are proven to be successful in monocular depth estimation,
  our network learns the geometric projection from aerial to ground, and
  to semantically segment the aerial images jointly.
  We present the learning details in \chapref{crosstransf}
  \newline

  \item \textbf{Location and Time as Pretext Task:}
  Smart devices like cellphones and webcams get more sophisticated
  nowadays. Most of them are equipped with clocks and GPS modules. Thanks to
  the development of social networks, researchers now can find
  large amount of images online that are tagged with time and
  geographic locations. In \chapref{whenwhere}, we propose an
  algorithm that treats the location and time as pretext tasks to learn
  useful image features.  By learning to predict the geographic location
  and the capture time of the query image, our network learns to extract
  geo-temporal features from the image.
